### 2022-11-12 NSF2022/Description/backgroundv3.tex
BG reworked

@@

\subsection{Problem formulation}
We recently developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
It takes ideas from the phase field method and leverages boundary
integral equations to resolve complex domains and speed up computations.
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).
Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is a rotation (proper orthogonal) $n
\times n$ matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equation~\eqref{eqn:stokes} is the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of the aqueous region with
viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$  etc.
representing metastable states of the solvent.
For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specific_aim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

For the moving domain boundary conditions,
equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
velocity $\omega_i$ (the axial vector for $R'_i(t)R_i(t)^T$)
about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at water-granule interface.
Finally, equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances that
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension,
$I$ is the $n\times n$ identity matrix,
and we define the ``cross product'' as
$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ when $\aa, \bb \in \mathbb{R}^2$.

We call the rigid bodies $U_i(t)$ granules since they are small, compact
parcels of a suspended media, e.g.~lipids, Janus spheres. We use the
shape and boundary conditions for $U_i$ to capture the local properties
of the suspended media. We have departed from the terminology
``particles'' to emphasize the role played by their finite size. In our
simulations (see \S\ref{sec:specific_aim1}), we include a finite length
repulsion to avoid particle collisions.

\begin{wrapfigure}[]{l}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss our planned approach in
Section~\ref{sec:specificaim2}.

@@

In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

In terms of mathematical justifications, we mention that when
equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, because of the introduction of granule boundaries,
interfacial energy enters the problem even in the linear case.
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

\begin{wrapfigure}[23]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-5pt}
  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)--(c) have
  the same initial configuration but different boundary conditions $g$.
  {Top Row:} Granules with an amphiphilic boundary condition
  results in a bilayer pattern shielding the hydrophobic core (yellow,
  $\eta > 0$) from the aqueous phase (blue, $\eta = 0$). {\em Middle
  Row:} Biased granules with a hydrophobic intensity that is greater on
  one side of the particle (magenta) than the other (yellow). {\em
  Bottom Row:} Bipolar granules where green is for $\eta < 0$, yellow is
  for $\eta > 0$, and blue is for $\eta = 0$. Particles orient like
  sides to form a checkerboard pattern.}
\end{wrapfigure}

\subsection{Applications}
Since the formulation is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example,
three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure~\ref{fig:flow_map}).
Moreover, a simple change
of boundary conditions from amphiphilic,
to biased hydrophobic, to polar
results in distinct equilibrium morphologies
(Figure~\ref{fig:self-assembly2}).
Further applications include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.

\subsection{Vesicles as self-organized granules}
\label{sec:vesicles_as_granules}
Interface problems coming from biology are a challenging
area of applied mathematics.  Broadly speaking, these problems
involve a fluid structure interaction where the modeler must
solve for the velocity in the aqueous phase, track the interface,
and couple the velocity boundary condition to the interface through
stress balance boundary conditions.  The aqueous phase can
be a low Reynolds-number fluid, a porous medium, or viscoelastic fluid,
and the interfacial forces can come from surface tension, elasticity,
or electrostatics.
Incorporating all these details can lead to models with substantial
complexity and there is a need for robust, general models that
cut across these issues.

This section shows the principles of PDE-driven
self-organization apply to the concrete
problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
Microscopically, the membrane of a vesicle is comprised
elongated amphiphilic lipids that form inner and outer monolayers.  
The goal in vesicle hydrodynamics is to study the flow patterns e.g.,
tank-treading, tumbling, that arrise due to the interaction
between membrane elasticity and surrounding fluid.
Traditional models represent a vesicle as a
continuous surface (or curve in $\mathbb{R}^2$) $\Sigma$.
The elastic energy takes the form
\begin{equation}
\label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS 
\end{equation}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
and $k_B$ is a bending modulus. 
The variation of \eqref{eq:Canham-Helfrich} with respect to position
gives rise to a surface force
that pointwise balances the jump in hydrodynamic stress across the interace.
While energy density does depend on Gaussian curvature,
it does not appear in \eqref{eq:Canham-Helfrich}
since Gauss-Bonnet Theorem guarantees that
the integral of Gaussian curvature over a closed surface is independent of the shape of $\Sigma$.

Depending on the situation,
one can further enforce constant volume constraints or permeability relationships.
If the interface is area incompressible, then the surface divergence
of velocity is zero.  On the other hand, if the surface is area compressible,
then \eqref{eq:Canham-Helfrich} contains an additional stretching term of the
form $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the
deformed and equilibrium area densitities respectively.

There are downsides to traditional models in terms of generality and physical realism.
(i) Motivated by drug delivery applications, experimenters use electric
fields, for example, to controllably open and close pores in membranes
\cite{}.
These kinds of topological changes are clumsy to incorporate in
sharp interface formulations that assume a continuous surface \cite{}.
(ii) Sharp-interface models assume a membrane of neglible thickness. 
However, in biological processes
like fusion, fission, or insertion and penetration by proteins and peptides, 
the length scales of the
deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm).
Moreover, these processes crucially rely on variable lipid
orientation relative to the surface normal (the so-called \emph{tilt}
deformation),
whereas \eqref{eq:Canham-Helfrich} implicitly assumes that the lipids
are everywhere normal to the surface.  
(iii) Finally, realistic membranes are comprised of a mixtures of lipids and proteins.
Recent work \cite{} has incorporated lipid mixtures in \eqref{eq:Canham-Helfrich},
but these models are formidably complicated 
due to the additional constraints and transport equations involved.

\begin{wrapfigure}[12]{r}{0.5\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-5pt}
\caption{\label{fig:amphiphilic_assembly}
Self-organization under amphiphilic boundary condition.
(a) Granules first match hydrophobic tails (red),
(b) then align length-wise.
The principle of self-organization holds in three dimensions 
as simulated by Kohl, Corona, and Veerapaneni
\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
Diffusive interface models and surface-director models partially address 
these shortcomings. 
Topological changes are permitted in phase field and level set formulations,
but these methods smear out the details of lipid orientations.
The detailed energies of lipid orientation that include tilt are
closely related to the celebraated and well-studied
field of nematic liquid crystals.  Here, there have been recent development
in simulation and theory of nematic liquid crystals on surfaces.
These models consider the interplay between defects and surface geometry \cite{},
finite element formulations \cite{}, and existence of minimizers \cite{}.

\subsubsection{Main modeling innovations}
We developed the model \eqref{eq:RBT}-\eqref{eqn:hydro_stress} 
as a robust and flexible approach
that cuts across many of the aforementioned challenges.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of vesicle morphology and topology--sufficiently
large forces will even pull the granules apart as physically required.
(ii) The model formulation is built around important details like lipid orientations,
and exhibits inter-monolayer slip that must be added into diffusive interface models
post hoc. 
(iii) It is straightforward to consider mixtures of granules with different
types of shapes and boundary conditions of the granules.
With the help of boundary integral equations
and fast summation methods, the dynamics can be solved in 
near-linear complexity in $N_b$, which is equal to or better than 
the computational complexity of related sharp interface methods.

Inspired
by the amphiphilic structure of lipids,
we formulated a so-called ``amphiphilic'' boundary condition
that leads a collection of granules to form bilayers.
Referring to Figure \ref{fig:amphiphilic_assembly}, 
\begin{equation}
\label{eq:amphiphilic_BC}
\phi(\mathbf{x}) = h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right), \quad
\mathbf{x} \in \Gamma_i,
\end{equation}
where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
``radius'' of the $i$th granule.  
The phase $\phi$ takes values close to $1$ on in the direction $\dd_i$,
representing a hydrophobic tail, and values close to $0$ 
in the direction $\dd_i$ representing the hydrophilic head.

\begin{figure}[t!]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/Background/coarsening.pdf}
\end{center}
\vspace{-20pt}
\caption{\label{fig:coarsening}
Modeling procedure.
We initilize a suspension of granules.
Under the moving domain problem
\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
with amphiphilic boundary condition, the granules
self-organize into vesicle bilayers.
We then introduce external hydrodynamic effects to study elastic properties.
}
\vspace{5pt}
\end{figure}
\subsubsection{How do granule-based vesicles have an elastic energy?}
A natural question to ask is how 
elastic energy enters a formulation
coming from surface interactions like \eqref{eqn:math_motivation}.
Conceptually, random suspensions of amphiphilic
granules undergo a rapid coarsening to form bilayers.
For tens of granule, the bilayers form a single stable, ring-shaped vesicle
with energy $E_{\text{stable}}$ (Figure \ref{fig:coarsening}, (c)).
This vesicle configuration, however, is only a local minimizer,
whereas the planar configuration (Figure \ref{fig:coarsening}, (e))
is the global minimizer.  The difference between
$E(t)$ and $E_{\min}$ is the vesicle elastic energy.
Indeed, if a background flow overcomes the energy barrier to force granules apart,
then the bilayer unfolds from its circular shape into a flat shape.

When hundreds granules are involved,
the two-dimensional granules reach an intermediate
state consisting of several bilayer segments (see Figure \ref{fig:self-assembly2}, top right).
Placing this metastable state into a mild background flow
causes the segments to join up into isolated vesicles \cite{fu-ryh-qua-you2022}.

Having a non-specific model that replicates detailed
physics and biology is the crown jewel of applied mathematics
and we believe that ours is such a model.

>>>>

We recently developed a new mathematical model of
self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
The framework uses small, rigid bodies called ``granules''
to represent parcels of a suspended media.
The granule shapes and boundary conditions
capture the local properties of the suspension,
and instead of volume fraction, a phase field function represents
the properties of the solvent.
Our approach falls into the category of work that considers
particles as a discretization of a continuous problem;
in this case one is dealing with a particle
method, as an alternative to other discretization methods
such as finite-difference, finite-element, and spectral methods
\cite{Wilson2021ComparisonOT}.
We have departed from the terminology
``particles'', though, to emphasize the role played the granules' finite size.

The framework is robust, flexible, and
cuts across many of the aforementioned challenges.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull granules apart as physically required.
(ii) The model formulation is built around important details like molecular orientations,
and exhibits inter-molecular slip that must be added into diffusive interface models
post hoc. 
(iii) It is straightforward to consider mixtures of granules with different
types of shapes and boundary conditions.
Leveraging boundary and fast summation methods, the dynamics can be solved in 
near-linear complexity in the number of granules,
which is equal to or better than 
the computational complexity of related sharp interface methods.

@@

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).
Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of
the incompressible fluid region with viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$  etc.
representing metastable states of the solvent.
For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specific_aim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

For the moving domain boundary conditions,
equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
velocity $\omega_i$ (the axial vector for $R'_i(t)R_i(t)^T$)
about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at water-granule interface.
Finally, equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances that
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension,
$I$ is the identity matrix,
and we define the ``cross product'' 
$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.

\begin{wrapfigure}[22]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-15pt}
  \caption{\footnotesize \label{fig:self-assembly2}
  Changes in the boundary condition \eqref{eqn:material}
  yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) = \tfrac{1}{2}\phi^2$.
  (\emph{Top}) Granules with an amphiphilic boundary condition
  results in a bilayer pattern (yellow,
  $\phi = 1$, blue, $\phi = 0$).
  (\emph{Middle}) Granules with $\phi = 2$ (magenta) on one side and $\phi = 1$
  on the other   form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = \pm 1$ (yellow, green, resp.)
  on poler ends   form a checkerboard pattern.}
\end{wrapfigure}
\subsection{Applications}
Since the framework is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}).
Changes in the boundary conditions result in
distint morphologies
(Figure~\ref{fig:self-assembly2})
whose rheology can be further investigate (\S\ref{subsec:specific_aim_3}).

A concrete application we have considered in our
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study the flow patterns 
that arrise due to the interaction
between membrane elasticity and the fluid.

A striking aspect of our hydrodynamic
simulation is its fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to realistic values,
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.

In terms of hydrodynamics, the granule vesicles in
background flows replicate
the behaviour of an continous, inextensible,
elastic vesicle with permeability.
The simulations showed, for the first time,
a granule-vesicle suspension behaving
as a tank-treading vesicle \cite{Finken2008, Shaqfeh11}
(see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal
intermonolayer slip and derived values for intermonolayer
friction were in good quantitative agreement 
those derived by atomistic and Martini force field
simulation studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}.
In Figure \ref{fig:JPv_rupture},
membrane rupture occurs at large shear rates 
and yields a dimensional scaling for 
critical rupture shear rate 
\cite{VLAHOVSKA2009775,keller_skalak_1982}.
A side-by-side comparison
of granule-based vesicles and the sharp interface
representation yielded shapes and trajectories that
overlapped.

\begin{wrapfigure}[10]{l}{0.46\textwidth}
\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
tank-treading in background shear flow.}
\end{wrapfigure}
Having a non-specific model that replicates physical details
is the crown jewel of applied mathematics.
\emph{Further applications} include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\newline

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[14]{r}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
\end{wrapfigure}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss in \S~\ref{sec:specificaim2}.

@@

\begin{wrapfigure}[10]{l}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}
In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

\subsection{Outline of the proposal}
The aim of this proposal is to advance the simulation
and theory for soft-matter systems
and foster training in mathematical sciences.
Section \ref{sec:BroaderImpacts} summarizes the broader
impacts and intellectual merit of our research activity.
Section \ref{sec:proposed-work} contains our
three specific aims.  They are
mathematical analysis of the system
(\S \ref{sec:specificaim1}: PI Ryham),
numerical implementation
(\S \ref{sec:specificaim2}: PI Quaife),
and  kinetic theory
(\S \ref{sec:specificaim3}: PI Young).
